Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and~Application

### 2023-10-16 Metals-2023-2.tex
Rename final production article

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{13}
\issuenum{10}
\articlenumber{1746}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: Zhanwei Yuan}
\datereceived{31 August 2023 }
\daterevised{10 October 2023 } % Comment out if no revised date
\dateaccepted{13 October 2023 }
\datepublished{15 October 2023 }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/10.3390/met13101746} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

% MDPI internal command: Title for citation in the left column
\TitleCitation{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and~Application}
%MDPI: Title modified, please confirm.
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453}
\newcommand{\orcidauthorB}{0000-0002-1522-2787}
\newcommand{\orcidauthorC}{0000-0002-5360-5121}
\newcommand{\orcidauthorD}{0000-0002-0815-1984}
\newcommand{\orcidauthorE}{0009-0004-1420-7552}

@@

% Keywords
\keyword{artificial neural network; constitutive flow law; Gleeble simulator; dynamic recrystallization; finite element analysis}

@@

As the occurrence of DRX softens the material, the~deformation loads during hot deformation must be adjusted from one pass to another to have a more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the~extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and~strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions, such as metallographic analysis~\cite{Babu-2022}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the~cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal~\cite{Peng-2022} determined the critical strain and critical stress for DRX's initiation based on the method proposed by Najafizadeh and Jonas~\cite{Najafizadeh-2006} to establish a DRX kinetic model for hot-rolled conditions based on the relationship between the characteristic parameters of DRX and the temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal~\cite{Gottstein-2004}, the~critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$, where $\sigma$ is the stress and $\varepsilon$ is the~strain.

@@

The raw stress--strain data were exported from the Gleeble thermomechanical simulator as true stress and true strain, and~the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure~\ref{fig:RawData}.
All stress--strain data are composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$ increments.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/rawData}
\caption{Stress--strain curves of medium-carbon alloy extracted from the Gleeble device for \mbox{5 temperatures} ($T$) and 6 strain rates ($\mdot\varepsilon$).}
\label{fig:RawData}
\end{figure}

@@

As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
One challenge is calculating the derivative of stress versus strain values numerically, as~compression test data exhibit oscillations, as~depicted in Figure~\ref{fig:RawData}.
It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.

To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver~\cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
\linebreak However, depending on the degree of the polynomial, for the same stress--strain curve, multiple solutions may be obtained.
This results in multiple possible forms for the $\theta(\sigma)$ function.

@@

Thus, for a $7-5$ network, $N_{int}=60$.
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two-hidden-layer artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was created with the dedicated Python library, Tensorflow~\cite{Abadi-2016}.
The training phase employed the Adaptive Moment Estimation (ADAM) optimizer~\cite{Kingma-2015}.
The training was conducted using 50,000~epochs of the experimental dataset.
It took approximately 15 min to train the ANN model and obtain the converged parameters on a Dell XPS-13 7390 %MDPI: Manufacturer Dell, City Toulouse, Country France. I don't know how to add it to the text.
 laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
\caption{Filtering of the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
\label{fig:AnnFit}
\end{figure}
\textls[-15]{A models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as~defined by the following equation:}
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$), as defined by the following equation:
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and~$N$ is the total number of data points used to compute those coefficients.
\linebreak For the proposed ANN filter, $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a 11{th} order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
\label{fig:AnnTheta}
\end{figure}
\unskip

@@

Secondly, %MDPI: Yes
 the~inflection point $\sigma_c$ can be obtained from the second derivative of $p(\sigma)$ with:
\begin{equation}
\frac{d^2 p(\sigma)}{d \sigma^2} = 0 \Longrightarrow \sigma_c = -a_1/3a_0
\end{equation}
Similarly, %MDPI:  Ok
 the~critical strain ($\varepsilon_c$) is calculated by defining a third-degree polynomial function $q(\sigma)$ approximating the $\ln \theta(\varepsilon)$ curve as depicted in Figure~\ref{fig:nThetaOP}:
\begin{equation}
q(\varepsilon) = b_0\varepsilon^3 + b_1\varepsilon^2 + b_2\varepsilon + b_3
\end{equation}

@@

The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure~\ref{fig:nDRX}, where a comparison between the experimental and predicted values is made for the strain rate $\mdot\varepsilon=0.001~\ps$ and three temperatures (1050 $^\circ$C, 1150 $^\circ$C and 1250 $^\circ$C).
\begin{figure}[H]
\centering
	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
	\caption{DRX experimental data (dots) and JMAK model-based prediction (plain lines).}
	\label{fig:nDRX}
\end{figure}
Figure~\ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, T = 1050 $^\circ$C, and $\varepsilon=0.55$. From~this, we determined the location of one experimental point in Figure~\ref{fig:nDRX} (the red one for $\varepsilon=0.55$). The~same approach using different temperatures and strains was used to obtain the other experimental points reported in Figure~\ref{fig:nDRX}.
\begin{figure}[H]
\centering
	\includegraphics[width=0.5\columnwidth]{Figures/micrograph}
	\caption{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050~^\circ$C, and $\varepsilon=0.55$.}
	\label{fig:eDRX}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Conv-ANN-6}
\caption{Evolution of the convergence of the models during the training procedure for the \mbox{6 proposed} network~architectures.}
\label{fig:ANN-conv}
\end{figure}
\unskip

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{
Conceptualization, P.T.M. and O.P.;
methodology, O.P.;
software, P.T.M. and O.P.;
validation, O.P.;
formal analysis, O.P. and P.D.;
investigation, P.D.;
resources, P.D. and M.J.;
data curation, P.T.M. and P.D.;
writing---original draft preparation, O.P. and P.T.M.;
writing---review and editing, O.P.;
visualization, O.P.;
supervision, M.J., A.T., and O.P.;
project administration, M.J.;
funding acquisition, M.J.
All authors have read and agreed to the published version of the~manuscript.}

@@

\conflictsofinterest{The authors declare no conflicts of~interest.}

@@

\bibitem[{Tize Mha} \em{et~al.}(2023){Tize Mha}, Dhondapure, Jahazi, Tongne,
  and Pantalé]{TizeMha-2023}
{Tize Mha}, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.
\newblock {Interpolation and Extrapolation Performance Measurement of
  Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium
  Carbon Steel}.
\newblock {\em Metals} {\bf 2023}, {\em 13}.
\newblock {\url{https://doi.org/10.3390/met13030633}}.

>>>>

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{13}
\issuenum{10}
\articlenumber{1746}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: Zhanwei Yuan}
\datereceived{31 August 2023 }
\daterevised{10 October 2023 } % Comment out if no revised date
\dateaccepted{13 October 2023 }
\datepublished{15 October 2023 }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/10.3390/\linebreak met13101746} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

% MDPI internal command: Title for citation in the left column
\TitleCitation{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and Application}
%MDPI: Title modified, please confirm.
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453}
\newcommand{\orcidauthorB}{0000-0002-1522-2787}
\newcommand{\orcidauthorC}{0000-0002-5360-5121}
\newcommand{\orcidauthorD}{0000-0002-0815-1984}
\newcommand{\orcidauthorE}{0009-0004-1420-7552}

@@

% Keywords
\keyword{\textls[-13]{artificial neural network; constitutive flow law; Gleeble simulator; dynamic recrystallization; finite element analysis}}

@@

\textls[-12]{As the occurrence of DRX softens the material, the~deformation loads during hot deformation must be adjusted from one pass to another to have a more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the~extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and~strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions, such as metallographic analysis~\cite{Babu-2022}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the~cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal~\cite{Peng-2022} determined the critical strain and critical stress for DRX's initiation based on the method proposed by Najafizadeh and Jonas~\cite{Najafizadeh-2006} to establish a DRX kinetic model for hot-rolled conditions based on the relationship between the characteristic parameters of DRX and the temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal~\cite{Gottstein-2004}, the~critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$, where $\sigma$ is the stress and $\varepsilon$ is the~strain.}

@@

The raw stress--strain data were exported from the Gleeble thermomechanical simulator as true stress and true strain, and~the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure~\ref{fig:RawData}.
All stress--strain data are composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$~increments.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/rawData}
\caption{Stress--strain curves of medium-carbon alloy extracted from the Gleeble device for \mbox{5 temperatures} ($T$) and 6 strain rates ($\mdot\varepsilon$).}
\label{fig:RawData}
\end{figure}

@@

\textls[-20]{As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
One challenge is calculating the derivative of stress versus strain values numerically, as~compression test data exhibit oscillations, as~depicted in Figure~\ref{fig:RawData}.
It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$~directly.}

\textls[-5]{To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver~\cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
\linebreak However, depending on the degree of the polynomial, for the same stress--strain curve, multiple solutions may be obtained.
This results in multiple possible forms for the $\theta(\sigma)$~function.}

@@

Thus, for a 7-5 network, $N_{int}=60$.
\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
\caption{Two-hidden-layer artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
\label{fig:ANN-7-5}
\end{figure}
The Python program used for training the neural network was created with the dedicated Python library, Tensorflow~\cite{Abadi-2016}.
The training phase employed the Adaptive Moment Estimation (ADAM) optimizer~\cite{Kingma-2015}.
The training was conducted using 50,000~epochs of the experimental dataset.
It took approximately 15 min to train the ANN model and obtain the converged parameters on a Dell XPS-13 7390 %MDPI: Manufacturer Dell, City Toulouse, Country France. I don't know how to add it to the text.
 laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/AnnFit}
\caption{Filtering of the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
\label{fig:AnnFit}
\end{figure}
\textls[-15]{A models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as~defined by the following equation:}
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the root-mean-squared error ($\RMSE$), as defined by the following equation:
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and~$N$ is the total number of data points used to compute those coefficients.
\linebreak For the proposed ANN filter, $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a 11{th} order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/AnnTheta}
\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
\label{fig:AnnTheta}
\end{figure}
\unskip

@@

Secondly, %MDPI: Yes
 the~inflection point $\sigma_c$ can be obtained from the second derivative of $p(\sigma)$ with:
\begin{equation}
\frac{d^2 p(\sigma)}{d \sigma^2} = 0 \Longrightarrow \sigma_c = -a_1/3a_0
\end{equation}

Similarly, %MDPI:  Ok
 the~critical strain ($\varepsilon_c$) is calculated by defining a third-degree polynomial function $q(\sigma)$ approximating the $\ln \theta(\varepsilon)$ curve as depicted in Figure~\ref{fig:nThetaOP}:
\begin{equation}
q(\varepsilon) = b_0\varepsilon^3 + b_1\varepsilon^2 + b_2\varepsilon + b_3
\end{equation}

@@

The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure~\ref{fig:nDRX}, where a comparison between the experimental and predicted values is made for the strain rate $\mdot\varepsilon=0.001~\ps$ and three temperatures (1050 $^\circ$C, 1150 $^\circ$C and 1250~$^\circ$C).
\begin{figure}[H]
\centering
	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
	\caption{DRX experimental data (dots) and JMAK model-based prediction (plain lines).}
	\label{fig:nDRX}
\end{figure}
Figure~\ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, T = 1050 $^\circ$C, and $\varepsilon=0.55$. From~this, we determined the location of one experimental point in Figure~\ref{fig:nDRX} (the red one for $\varepsilon=0.55$). The~same approach using different temperatures and strains was used to obtain the other experimental points reported in Figure~\ref{fig:nDRX}.
\begin{figure}[H]
\centering
	\includegraphics[width=0.5\columnwidth]{Figures/micrograph}
	\caption{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050~^\circ$C, and $\varepsilon=0.55$.}
	\label{fig:eDRX}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.75\columnwidth]{Figures/Conv-ANN-6}
\caption{Evolution of the convergence of the models during the training procedure for the \mbox{6 proposed} network~architectures.}
\label{fig:ANN-conv}
\end{figure}
\unskip

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{
Conceptualization, P.T.M. and O.P.;
methodology, O.P.;
software, P.T.M. and O.P.;
validation, O.P.;
formal analysis, O.P. and P.D.;
investigation, P.D.;
resources, P.D. and M.J.;
data curation, P.T.M. and P.D.;
writing---original draft preparation, O.P. and P.T.M.;
writing---review and editing, O.P.;
visualization, O.P.;
supervision, M.J., A.T. and O.P.;
project administration, M.J.;
funding acquisition, M.J.
All authors have read and agreed to the published version of the~manuscript.}

@@

\conflictsofinterest{The authors declare no conflict of~interest.}

@@

\bibitem[{Tize Mha} \em{et~al.}(2023){Tize Mha}, Dhondapure, Jahazi, Tongne,
  and Pantalé]{TizeMha-2023}
{Tize Mha}, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.
\newblock {Interpolation and Extrapolation Performance Measurement of
  Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium
  Carbon Steel}.
\newblock {\em Metals} {\bf 2023}, {\em 13}, 633.
\newblock {\url{https://doi.org/10.3390/met13030633}}.
